\documentclass{iiser-thesis}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb, amsthm, thmtools, amsfonts}
\usepackage[dvipsnames]{xcolor}
%Command for theorems and stuff
\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{plain}
\newtheorem{definition}[theorem]{Definition}
\declaretheorem[style = plain, qed = $\lozenge\blacklozenge\lozenge$, numberwithin = section]{example}
%tikzpicture
\usepackage{tikz}
\usepackage{scalerel}
\usepackage{pict2e}
\usepackage{tkz-euclide}
\usetikzlibrary{calc}
\usetikzlibrary{patterns,arrows.meta}
\usetikzlibrary{shadows}
\usetikzlibrary{external}
\usepackage{tikz-cd}

%pgfplots
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepgfplotslibrary{statistics}
\usepgfplotslibrary{fillbetween}
\usepackage[framemethod=TikZ]{mdframed}
%references package
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    allcolors=blue}

%Thesis Preamble

\title{Tropical and Algebraic Geometry}
\author{Aditya Marodia}
\coordinator{Coordinator} \supervisor{Dr. Vivek Mohan Mallick} \sdesignation{Associate Professor}
\department{Department of Mathematics} \reader{Dr. Amit Hogadi}
%\reader{Reader 2}
\dedication{This thesis is dedicated to hm}ematician at the University of Texas, Austin, published a paper in August that used tropical geometry to establish a link between shapes and equations.
\graduationyear{2025}
\academicyear{2024-2025}
\graduationmonth{May}

\thesisabstract{
    Over the past few deccades Tropical Geometry has emerged as an enticing subfield of Algebraic Geometry. 
    In Tropical Geometry one often deals with combinatorial objects which come from algebraic varieties - retaining a lot of their original structure.
    In this thesis we look at Tropical Geometry and see how one can use Tropical methods to solve problems in Algebraic Geometry.
    The primary problem we look at in this thesis is the curve counting problem: how many curves of degree $d$ pass through $3d-1$ points in the plane?
    We study the original proof of this problem, given by Maxim Kontsevich - using the moduli space of stable maps.
    Then we allude to Mikhailkin's correspondence result, which showed that these numbers are the same in the Tropical world.
    We then look at proof of this result in the Tropical world and compare the methods used in this proof to those of Kontsevich's.
}
\acknowledgments{Not more than 250 words}

%Start of document
\begin{document}

\thesisfront


\chapter{Preliminaries on tropical geometry}
\label{chap:sturmfels}
\input{Chapters/tropicalIntro.tex}

%\chapter{Some algebraic geometry}
%\label{chap:alggeom}
%\input{Chapters/agIntro.tex}

\chapter{Kontsevich formula in algebraic geometry}
\label{chap:kontalggeom}
\input{Chapters/kontFormInAG.tex}

\chapter{Kontsevich formula in tropical geometry}
\label{chap:kottropgeom}

\chapter{Conclusion}
\label{chap:conclusion}
aaaaa
\bibliographystyle{alpha}
\bibliography{References}
\end{document}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
